NumPy---Array Programming in Python

### 2020-01-24 body.tex
Add quote about APL users

>>>>

This description of how APL users work easily applies to scientific Python
users \cite{kromberg2007apl}:
\begin{quote}
Users of APL tend to ``live in their data''. Interactive interpreters allow them
to inspect, almost feel their  way forward, discovering successful snippets
of code through experimentation and collecting them
into imperative or functional programs according to taste.
\end{quote}
